### 2016-07-06 paper/paper.tex
Added the paper.

\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{cite}
\usepackage[cmex10]{amsmath}

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
% This package may be useful when used in conjunction with IEEEtran.cls'
% captionsoff option. Some IEEE journals/societies require that submissions
% have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.3.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% For subfigure.sty:
% \let\MYorigsubfigure\subfigure
% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat/subfig command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{An interactive environment for mapping comutational structures to FPGAs}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Rinse~Wester~and~Robert~de~Groote}

% make the title area
\maketitle

\begin{abstract}
  In this paper we propose a methodology to translate computational structures to hardware.
  Computational structures express both the computation and the ordering of computations.
  These structures are expressed using datalfow graph from which hardware can be generated more direclty compared to imperative apporaches.
  As a proof of concept, SDFkit is developed.
  SDFkit is a cycle accurate simulation environment for these computational structures and has a backend to generate highliy parallel FPGA code.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Strucutre, Computations, FPGA, SDFkit
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}

  FPGAs have an enormous potential in terms of computational power.
  However, they still remain hard to program even though a lot of work has been performed on translating imperative languages to hardware.
  By using a sequential language to descibe parallel hardware a structural mismatch emerges.
  A lot of analysis is therefore requiered to determine which computations are independant and ca therefore be performed in parallel.

  In this work-in-progress paper, we propose a more strucutral approach to computations.
  method..... math descrition to CSDF graph/ transformations to make efficient hardware then HW generation

  The cuccrent implementation: SFDkit, an interactive environment

\section{Approach}

  Computational strucutres borrowed from functional porgramming languages so called higher-order functions.
  These functions are very suitable to express the strucutre in computations and therefore a good source of parallelism.
  \todo{ref to thesis Rinse}
  These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
  Transformations are then applied to this graph to optimize performance.
  \todo{ref naar thesis Robert}
  During the final step, the graph is mapped to hardware by translating each node to a combinational component and repacing the edges by a FIFO.

  \todo[inline]{elaborate a bit... big data programmers are already familiar with a structural approach to programming like hadoop}

\section{Results}

  \todo[inline]{Robert, kun je hier wat vertellen over de transformaties van computational structures naar CSDF graphs en bijbehorende transformaties.}

  \todo[inline]{decribe status of SDFkit}

  Figure \ref{fig:screenshot} shows a screenshot of SDFkit.
  The central widget shows a visualisation of a CSDF graph which can be simulated in a step-wise fashion using the control panel on the left.
  For debugging purposes, the data contained in each token for each simulation step is visualised in the lower widget.

  \begin{figure}[h]
    \centering
    \includegraphics[width=2.5in]{screenshot.png}
    \caption{Screenshot of SDFkit}
    \label{fig:screenshot}
  \end{figure}

  \todo[inline]{describe the current status of the hardware generation process}

\section{Conclusion}

  In this paper we presented SDFkit, an interactive environment for designing applications using SDF graphs.
  In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a comptation.
  Using these computational structures, the generation of highly parallel hardware is tremendously simplyfied.
  Applications are modeled using CSDF graphs which are a cycle-accurate model for the generated hardware.
  \todo[inline]{extend conslusion a bit with current state of project}

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

\end{document}

### 2016-07-06 paper/paper.tex
performed a spell check.

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{An interactive environment for mapping comutational structures to FPGAs}
+\title{An interactive environment for mapping computational structures to FPGAs}
 %
@@
   Computational structures express both the computation and the ordering of computations.
-  These structures are expressed using datalfow graph from which hardware can be generated more direclty compared to imperative apporaches.
+  These structures are expressed using dataflow graph from which hardware can be generated more directly compared to imperative approaches.
   As a proof of concept, SDFkit is developed.
-  SDFkit is a cycle accurate simulation environment for these computational structures and has a backend to generate highliy parallel FPGA code.
+  SDFkit is a cycle accurate simulation environment for these computational structures and has a backend to generate highly parallel FPGA code.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Strucutre, Computations, FPGA, SDFkit
+  Structure, Computations, FPGA, SDFkit
 \end{IEEEkeywords}
@@
   However, they still remain hard to program even though a lot of work has been performed on translating imperative languages to hardware.
-  By using a sequential language to descibe parallel hardware a structural mismatch emerges.
-  A lot of analysis is therefore requiered to determine which computations are independant and ca therefore be performed in parallel.
+  By using a sequential language to describe parallel hardware a structural mismatch emerges.
+  A lot of analysis is therefore required to determine which computations are independent and ca therefore be performed in parallel.
 
-  In this work-in-progress paper, we propose a more strucutral approach to computations.
-  method..... math descrition to CSDF graph/ transformations to make efficient hardware then HW generation
+  In this work-in-progress paper, we propose a more structural approach to computations.
+  method..... math description to CSDF graph/ transformations to make efficient hardware then HW generation
 
-  The cuccrent implementation: SFDkit, an interactive environment
+  The current implementation: SDFkit, an interactive environment...
+
+  Describe what is presented in remainder of paper..
 
@@
 
-  Computational strucutres borrowed from functional porgramming languages so called higher-order functions.
-  These functions are very suitable to express the strucutre in computations and therefore a good source of parallelism.
+  Computational structures borrowed from functional programming languages so called higher-order functions.
+  These functions are very suitable to express the structure in computations and therefore a good source of parallelism.
   \todo{ref to thesis Rinse}
@@
   \todo{ref naar thesis Robert}
-  During the final step, the graph is mapped to hardware by translating each node to a combinational component and repacing the edges by a FIFO.
+  During the final step, the graph is mapped to hardware by translating each node to a combinational component and replacing the edges by a FIFO.
 
@@
 
-  \todo[inline]{decribe status of SDFkit}
+  \todo[inline]{describe status of SDFkit}
 
   Figure \ref{fig:screenshot} shows a screenshot of SDFkit.
-  The central widget shows a visualisation of a CSDF graph which can be simulated in a step-wise fashion using the control panel on the left.
-  For debugging purposes, the data contained in each token for each simulation step is visualised in the lower widget.
+  The central widget shows a visualization of a CSDF graph which can be simulated in a step-wise fashion using the control panel on the left.
+  For debugging purposes, the data contained in each token for each simulation step is visualized in the lower widget.
 
@@
   In this paper we presented SDFkit, an interactive environment for designing applications using SDF graphs.
-  In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a comptation.
-  Using these computational structures, the generation of highly parallel hardware is tremendously simplyfied.
+  In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a computation.
+  Using these computational structures, the generation of highly parallel hardware is tremendously simplified.
   Applications are modeled using CSDF graphs which are a cycle-accurate model for the generated hardware.
-  \todo[inline]{extend conslusion a bit with current state of project}
+  \todo[inline]{extend conclusion a bit with current state of project}
 

### 2016-07-06 paper/paper.tex
Worked on intro and added bib file and makefile.

@@
   In this work-in-progress paper, we propose a more structural approach to computations.
-  method..... math description to CSDF graph/ transformations to make efficient hardware then HW generation
+  As input, a mathematical description of the application is given which is transformed into a CSDF graph.
+  Transformations to enhance performance are then applied to this graph.
+  A cycle accurate simulation gives insight into where the bottlenecks of the application are.
+  Finally, when the performance of the graph is sufficient, the graph is translated to hardware.
 
-  The current implementation: SDFkit, an interactive environment...
+  As a proof of concept to show the effectiveness of the approach, an interactive environment for simulation and hardware generation  is being developed named SDFkit.
+  Using SDFkit, CSDF graphs can be visualized and simulated in a cycle accurate manner.
+  Additionally, using the code can be generated for FPGAs.
 
-  Describe what is presented in remainder of paper..
+  The remainder of this paper is organized as follows:
+  First, the approach is covered in Section \ref{sec:approach} after which results are covered in Section \ref{sec:results}.
+  Finally, conclusion and future work are expressed in Section \ref{sec:conclusions}.
 
 \section{Approach}
+\label{sec:approach}
 
@@
   These functions are very suitable to express the structure in computations and therefore a good source of parallelism.
-  \todo{ref to thesis Rinse}
+  \todo{ref to thesis Rinse \cite{Wester15}}
   These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
   Transformations are then applied to this graph to optimize performance.
-  \todo{ref naar thesis Robert}
+  \todo{ref naar thesis Robert \cite{deGroote16}}
   During the final step, the graph is mapped to hardware by translating each node to a combinational component and replacing the edges by a FIFO.
@@
 
+  \todo[inline]{mention CLaSH \cite{Baaij10} as used for backend}
+
 \section{Results}
+\label{sec:results}
 
@@
 
-\section{Conclusion}
+\section{Conclusions and future work}
+\label{sec:conclusions}
 
@@
   Applications are modeled using CSDF graphs which are a cycle-accurate model for the generated hardware.
+
   \todo[inline]{extend conclusion a bit with current state of project}
+
+  \todo[inline]{Future work: Complete support for CSDF, hierarchy is design environment, multicore and GPU code generation}
 
@@
 % (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
+% \begin{thebibliography}{1}
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+% \bibitem{IEEEhowto:kopka}
+% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
 
-\end{thebibliography}
+%   \bibliographystyle{unsrt}
+% {\small\bibliography{biblio}}
+
+% \end{thebibliography}
+
+% bibliography{IEEEabrv,biblio}
+
+\bibliographystyle{unsrt}
+\bibliography{biblio}
 

### 2016-07-07 paper/paper.tex
More or less completed the intro and conclusions

@@
 \usepackage[cmex10]{amsmath}
+
+\newcommand{\clash}{C$\lambda$aSH}
 
@@
 
-\author{Rinse~Wester~and~Robert~de~Groote}
+\author{Rinse~Wester~and~Robert~de~Groote \\CAES group, EEMCS\\ University of Twente\\ \{r.wester, robert.degroote\}@utwente.nl}
 
@@
   Computational structures borrowed from functional programming languages so called higher-order functions.
-  These functions are very suitable to express the structure in computations and therefore a good source of parallelism.
-  \todo{ref to thesis Rinse \cite{Wester15}}
+  These functions are very suitable to express the structure in computations and therefore a good source of parallelism~\cite{Wester15}.
   These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
-  Transformations are then applied to this graph to optimize performance.
-  \todo{ref naar thesis Robert \cite{deGroote16}}
+  Transformations are then applied to this graph to optimize performance~\cite{deGroote16}.
   During the final step, the graph is mapped to hardware by translating each node to a combinational component and replacing the edges by a FIFO.
 
-  \todo[inline]{elaborate a bit... big data programmers are already familiar with a structural approach to programming like hadoop}
-
-  \todo[inline]{mention CLaSH \cite{Baaij10} as used for backend}
+  \begin{itemize}
+    \item computational structures: \todo[inline]{elaborate a bit... big data programmers are already familiar with a structural approach to programming like hadoop}
+    \item CSDF graphs and transformations
+    \item simulation
+    \item hardware generation using \clash \cite{Baaij10}
+  \end{itemize}
 
@@
 
-  \todo[inline]{Robert, kun je hier wat vertellen over de transformaties van computational structures naar CSDF graphs en bijbehorende transformaties.}
+  \todo[inline]{Robert, kun je hier wat vertellen over de transformaties van computational structures naar CSDF graphs en bijbehorende transformaties, inclusief voorbeeld}
 
@@
 
-  \begin{figure}[h]
+  \begin{figure}[h!]
     \centering
-    \includegraphics[width=2.5in]{screenshot.png}
+    \includegraphics[width=3in]{screenshot.png}
     \caption{Screenshot of SDFkit}
@@
 
-  \todo[inline]{extend conclusion a bit with current state of project}
+  As a proof of concept, an interactive simulation and hardware generation environment named SDFkit is being developed.
+  Currently, SDFkit supports visualization and simulation of HSDF, SDF and CSDF graphs.
+  Additionally, \clash code can be generated for HSDF graphs.
 
-  \todo[inline]{Future work: Complete support for CSDF, hierarchy is design environment, multicore and GPU code generation}
+  The next step in development is to extend the hardware code generation with support for SDF and CSDF graphs.
+  Additionally, the transformations to make a tradeoff between space and time are now performed outside SDFkit.
+  Integration of these transformations into SDFkit is therefore an other important step forward.
+  Finally, Interesting opportunities lie in extending the backend with a wider range of supported platform like C code and OpenCL.
 

### 2016-07-07 paper/paper.tex
making progress on approach section.

@@
 
-  Computational structures borrowed from functional programming languages so called higher-order functions.
+  Computational structures are borrowed from functional programming languages so called higher-order functions.
   These functions are very suitable to express the structure in computations and therefore a good source of parallelism~\cite{Wester15}.
@@
 
-  \begin{itemize}
-    \item computational structures: \todo[inline]{elaborate a bit... big data programmers are already familiar with a structural approach to programming like hadoop}
-    \item CSDF graphs and transformations
-    \item simulation
-    \item hardware generation using \clash \cite{Baaij10}
-  \end{itemize}
+  The main advantage of using computational structures is that there is no need to perform dependency analysis of for-loops.
+  Since all dependencies are known, computations can be distributed over space and time by mathematical transformation rules.
+  Even though no standard C for-loops are used to express repettive computations, this should not be a problem for programmers since similar patters are also used in map-reduce applications.
+  Figure XXXXXXX shows two examples of computational structures: the higher-order function \emph{zipWith} and \emph{foldl}.
+  Using \emph{zipWith} an operation is applied to pairs from two lists while \emph{foldl} reduces all elements in a list to one element.
+
+  \missingfigure{plaatje zipw en foldl hier}
+
+  \todo[inline]{Robert, kun je hier wat vertellen over de transformaties van computational structures naar CSDF graphs en bijbehorende transformaties, inclusief voorbeeld}
+
+  In order to determine accuracte perfomance metric of an application, the simulation must be accurate.
+  In SDFkit, the simulation can be used to for verify functional correctness as wel as performance.
+  Due to a specific mapping of the application graph to hardware, a cycle accurate simulation can be performed.
+  Additionally, the tokens on the edges can be changed any time allowing the user to identify bottlenecks in the graph and to tweak performance.
+
+  \todo[inline]{hardware generation using \clash \cite{Baaij10}}
+  nodes becaome combinational components and adges are implemented as FIFOs.....
+  The code is generated using \clash, a fundtional hardware description language.
+  each node has a peace of \clash code that represents the functionality of the node.....
 
@@
 \label{sec:results}
-
-  \todo[inline]{Robert, kun je hier wat vertellen over de transformaties van computational structures naar CSDF graphs en bijbehorende transformaties, inclusief voorbeeld}
 
@@
 
-  In this paper we presented SDFkit, an interactive environment for designing applications using SDF graphs.
+  In this paper we presented a methodology for designing hardware using a structured approach.
   In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a computation.

### 2016-07-07 paper/paper.tex
Bit of a spell check was needed.

@@
   Since all dependencies are known, computations can be distributed over space and time by mathematical transformation rules.
-  Even though no standard C for-loops are used to express repettive computations, this should not be a problem for programmers since similar patters are also used in map-reduce applications.
+  Even though no standard C for-loops are used to express repetitive computations, this should not be a problem for programmers since similar patters are also used in map-reduce applications.
   Figure XXXXXXX shows two examples of computational structures: the higher-order function \emph{zipWith} and \emph{foldl}.
@@
 
-  In order to determine accuracte perfomance metric of an application, the simulation must be accurate.
-  In SDFkit, the simulation can be used to for verify functional correctness as wel as performance.
+  In order to determine accurate performance metric of an application, the simulation must be accurate.
+  In SDFkit, the simulation can be used to for verify functional correctness as well as performance.
   Due to a specific mapping of the application graph to hardware, a cycle accurate simulation can be performed.
@@
   \todo[inline]{hardware generation using \clash \cite{Baaij10}}
-  nodes becaome combinational components and adges are implemented as FIFOs.....
-  The code is generated using \clash, a fundtional hardware description language.
+  nodes become combinational components and edges are implemented as FIFOs.....
+  The code is generated using \clash, a functional hardware description language.
   each node has a peace of \clash code that represents the functionality of the node.....

### 2016-07-07 paper/paper.tex
Added figure about HOFs
Wrote paragraph about hardware generation.

@@
   Even though no standard C for-loops are used to express repetitive computations, this should not be a problem for programmers since similar patters are also used in map-reduce applications.
-  Figure XXXXXXX shows two examples of computational structures: the higher-order function \emph{zipWith} and \emph{foldl}.
+  Figure \ref{fig:zipwthandfoldlstruct} shows two examples of computational structures: the higher-order function \emph{zipWith} and \emph{foldl}.
   Using \emph{zipWith} an operation is applied to pairs from two lists while \emph{foldl} reduces all elements in a list to one element.
 
-  \missingfigure{plaatje zipw en foldl hier}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[width=3in]{HOFs}
+    \caption{Structure of \emph{zipWith} and \emph{foldl}}
+    \label{fig:zipwthandfoldlstruct}
+  \end{figure}
 
@@
 
-  \todo[inline]{hardware generation using \clash \cite{Baaij10}}
-  nodes become combinational components and edges are implemented as FIFOs.....
-  The code is generated using \clash, a functional hardware description language.
-  each node has a peace of \clash code that represents the functionality of the node.....
+  During hardware generation, each node is implemented as a combinational circuit containing the functionality of the node and logic for producing and consuming data.
+  The edges, on the other hand, are implemented as FIFOs.
+  The code is generated using \clash, a functional hardware description language~\cite{Baaij10}.
+  Additional to the python code that can be put in a node for simulation, \clash\ code is added for the implementation on hardware.
 

### 2016-07-07 paper/csdf-dp.tex
Plaatje CSDF

\begin{tikzpicture}[xscale=0.7]

\tikzstyle{sdfgnode} = [circle,draw=black,draw opacity=0.7,fill=yellow!30,fill opacity=0.9,inner sep=0,minimum width=14pt,font=\scriptsize,text=black,text opacity=1]%
\tikzstyle{sdfgdata} = [sdfgnode, inner sep=1pt,fill=blue!60!black,fill opacity=0.4]%
\tikzstyle{sdfgmem} = [sdfgnode, rectangle, rounded corners=4pt, inner sep=2pt,fill=blue!60!black,fill opacity=0.1]%
\tikzstyle{sdfgarc} = [->,minimum width=1pt,>=latex,sloped]%
\tikzstyle{token} = [circle,inner sep=0,draw=black,fill=black,minimum size=5pt]%
\tikzstyle{rate} = [inner sep=2pt,font=\footnotesize]%
\tikzstyle{bb} = [rectangle, draw=black!20, dashed]%

\node[sdfgdata] (xs) at (-1.5, 1) {$xs$};
\node[sdfgdata] (ys) at (-1.5, -1) {$ys$};
\node[sdfgnode] (mul) at (0.5, 0) {$\times$};

\node[sdfgdata] (a) at (3.5, 1) {0};
\node[sdfgnode] (f) at (6, 0) {$+$};
\node[sdfgdata] (w) at (9, 0) {$dp$};
%\node[sdfgdata] (x) at (2.5, 0) {$ps$};

\draw[sdfgarc] (xs) --
    node[pos=0.0,sloped,rate,anchor=south west] {$\langle n * 1 \rangle$}
    +(1.5, 0) --
    node[pos=0.4,sloped=false,rate,anchor=south west] {$\langle n * 1 \rangle$}
    (mul);

\draw[sdfgarc] (ys) --
    node[pos=0.0,sloped,rate,anchor=south west] {$\langle n * 1 \rangle$}
    +(1.5, 0) --
    node[pos=0.4,sloped=false,rate,anchor=north west] {$\langle n * 1 \rangle$}
    (mul);

\draw[sdfgarc] (mul) --
    node[pos=0.0,sloped,rate,anchor=south west] {$\langle n * 1 \rangle$}
    node[pos=1.0,sloped=false,rate,anchor=south east] {$\langle n * 1 \rangle$}
    (f);

\draw[sdfgarc] (a) --
    node[pos=0.0,sloped,rate,anchor=south west] {$1$}
    +(2, 0) --
    node[pos=0.4,sloped=false,rate,anchor=south west] {$\langle 1, n * 0 \rangle$}
    (f);

%\draw[sdfgarc] (x) --
%    node[pos=0.0,sloped,rate,anchor=south west] {$\langle n * 1 \rangle$}
%    node[pos=0.9,sloped=false,rate,anchor=south east] {$\langle 0, n * 1 \rangle$}
%    (f);

\draw[sdfgarc] (f) --
    node[pos=0.0,rate,anchor=south west] {$\langle n * 0, 1 \rangle$}
    node[pos=1.0,rate,anchor=south east] {$1$}
    (w);

\begin{scope}[scale=0.8]
\draw[sdfgarc] (f)
    .. controls ($(f) + (-50:1)$) and ($(f) + (0.5,-1)$) .. ($(f) + (0, -1)$)
    node[pos=0.3, sloped=false, rate, anchor=south west, font=\tiny] {$ \langle n * 1, 0 \rangle $}
    .. controls ($(f) + (-0.5,-1)$) and ($(f) + (-130:1)$) ..
    node[pos=0.7, sloped=false, rate, anchor=south east, font=\tiny] {$ \langle 0, n * 1 \rangle $}
    (f);
\end{scope}

\end{tikzpicture}

### 2016-07-07 paper/paper.tex
Plaatje CSDF

@@
 \usepackage[cmex10]{amsmath}
+\usetikzlibrary{calc,positioning}
 
@@
 
-  \todo[inline]{Robert, kun je hier wat vertellen over de transformaties van computational structures naar CSDF graphs en bijbehorende transformaties, inclusief voorbeeld}
+  Functional specifications of computations can be represented by CSDF graphs using a straightforward translation.
+  As an example, consider the functional specification of a simple dot product of two vectors, written in the functional programming language Haskell.
+
+dot\_product xs ys = fold (+) 0 (zipWith (*) xs ys)\todo{Use nice listing environment}
+
+  The CSDF graph representation of this specification is depicted in Figure~\ref{fig:csdf-dotproduct}.
+  \begin{figure}[h!]
+    \centering
+    \input{csdf-dp}
+    \caption{Cyclo-static dataflow graph representation of dot-product}
+    \label{fig:csdf-dotproduct}
+  \end{figure}
 

### 2016-07-07 paper/paper.tex
Described current state of SDFkit

--- 2016-07-07 paper/paper.tex
@@
 
-  \todo[inline]{describe status of SDFkit}
+  Currently, SDFkit can import graphs expressed in a JSON file format.
+  These files contain a list of nodes and edges.
+  Additionally, each node contains a python lambda expression for the functional behavior of the node during simulation.
+  After opening, both the functionality of the nodes and data on the edges can be altered using the GUI.
 

### 2016-07-07 paper/paper.tex
Text update CSDF transformaties

--- 2016-07-07 paper/paper.tex
@@
   The CSDF graph representation of this specification is depicted in Figure~\ref{fig:csdf-dotproduct}.
+  Each node in the graph represents a function, where function is to be interpreted in the widest sense: we regard values simply as functions that take no argument.
+  The node corresponding to the addition has a self-loop, which indicates that it is involved in a \emph{stateful} computation - the fold.
+  Note that neither of the two higher-order functions that appear in the specification (fold and zipWith) are represented by nodes in the CSDF graph.
+  Higher-order functions do not map to individual nodes, but rather to \emph{subgraphs}.
+  In general, the CSDF graphs derived from functional specifications are \emph{hierarchical}.
+  That is, one may collapse a subgraph into a single node, which makes the higher-order functions explicit.
   \begin{figure}[h!]
@@
   \end{figure}
+
+  Each node in the CSDF graph represents a function that is computed at a particular \emph{place} - a location in space, such as a processing element, or an input port.
+  Performing the computation on actual values corresponds to \emph{executing} the CSDF graph.
+  During such an execution, each node may be invoked several times, at different time instants.
+
+  By applying an \emph{unfolding} transformation to the graph, a node is replaced by several copies, each representing a subset of the invocations of that node.
+  This increases the space allocatd to that function, and decreases the number of node invocations per place.
+  It furthermore explicitly exposes parallelism, which may be beneficial to performance.
 

### 2016-07-07 paper/paper.tex
Wrote the part on the current state of the hardware generation.

--- 2016-07-07 paper/paper.tex
@@
   Functional specifications of computations can be represented by CSDF graphs using a straightforward translation.
-  As an example, consider the functional specification of a simple dot product of two vectors, written in the functional programming language Haskell.
+  As an example, consider the functional specification of a simple dot product of two vectors, written in the functional programming language Haskell:
 
-dot\_product xs ys = fold (+) 0 (zipWith (*) xs ys)\todo{Use nice listing environment}
+\begin{verbatim}
+  dotprod xs ys = 
+      fold (+) 0 (zipWith (*) xs ys)  
+\end{verbatim}
 
@@
 
-  In order to determine accurate performance metric of an application, the simulation must be accurate.
+  In order to determine accurate performance metrics of an application, the simulation must be accurate.
   In SDFkit, the simulation can be used to for verify functional correctness as well as performance.
@@
 
-  \todo[inline]{describe the current status of the hardware generation process}
+  Currently, the hardware generation backend only supports HSDF graphs, i.e., the most simple type of SDF graph.
+  To add support for complete SDF and CSDF graphs, the edges have to support storing a variable amount of tokens each clock cycle.
+  This is in terms of hardware much more complicated.
 

### 2016-07-07 paper/paper.tex
A few spelling checks

@@
   By using a sequential language to describe parallel hardware a structural mismatch emerges.
-  A lot of analysis is therefore required to determine which computations are independent and ca therefore be performed in parallel.
+  A lot of analysis is therefore required to determine which computations are independent and can therefore be performed in parallel.
 
@@
   By applying an \emph{unfolding} transformation to the graph, a node is replaced by several copies, each representing a subset of the invocations of that node.
-  This increases the space allocatd to that function, and decreases the number of node invocations per place.
+  This increases the space allocated to that function, and decreases the number of node invocations per place.
   It furthermore explicitly exposes parallelism, which may be beneficial to performance.

### 2016-07-07 paper/paper.tex
Paar intro-aanpassinkjes, CSDF ref toegevoegd

@@
   However, they still remain hard to program even though a lot of work has been performed on translating imperative languages to hardware.
-  By using a sequential language to describe parallel hardware a structural mismatch emerges.
-  A lot of analysis is therefore required to determine which computations are independent and can therefore be performed in parallel.
-
-  In this work-in-progress paper, we propose a more structural approach to computations.
-  As input, a mathematical description of the application is given which is transformed into a CSDF graph.
+  Imperative languages have evolved around \emph{sequential} machines.
+  Using such a language to describe parallel hardware therefore causes a mismatch in \emph{structue}.
+  Rather than resolving this mismatch using complex dependency analyses, we propse, in this work-in-progress-paper, a \emph{structural} approach to computations.
+  In our approach, we take as input a mathematical\todo{Functional, declarative?} description of the application, and transform it into a \emph{cyclo-static dataflow} (CSDF) graph~\cite{bilsen1996}.
   Transformations to enhance performance are then applied to this graph.
@@
   These functions are very suitable to express the structure in computations and therefore a good source of parallelism~\cite{Wester15}.
-  These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
+  These computational structures are represented as a specific kind of dataflow graph, a cyclo-static dataflow (CSDF) graph.
   Transformations are then applied to this graph to optimize performance~\cite{deGroote16}.
@@
     \input{csdf-dp}
-    \caption{Cyclo-static dataflow graph representation of dot-product}
+    \caption{Cyclo-static dataflow graph representation of dot-product.}
     \label{fig:csdf-dotproduct}
@@
 
-  Currently, the hardware generation backend only supports HSDF graphs, i.e., the most simple type of SDF graph.
-  To add support for complete SDF and CSDF graphs, the edges have to support storing a variable amount of tokens each clock cycle.
+  Currently, the hardware generation backend only supports \emph{homogeneous} SDF (HSDF) graphs, which is the simplest type of SDF graph.
+  To add support for complete CSDF graphs, the edges have to support storing a variable amount of tokens each clock cycle.
   This is in terms of hardware much more complicated.

### 2016-07-07 paper/paper.tex
Squeezed it into two pages.

@@
   Computational structures express both the computation and the ordering of computations.
-  These structures are expressed using dataflow graph from which hardware can be generated more directly compared to imperative approaches.
+  These structures are expressed using dataflow graphs from which hardware can be generated more directly compared to imperative approaches.
   As a proof of concept, SDFkit is developed.
-  SDFkit is a cycle accurate simulation environment for these computational structures and has a backend to generate highly parallel FPGA code.
+  SDFkit is a cycle accurate simulation environment for these computational structures and has a backend to generate FPGA code.
 \end{abstract}
@@
   Imperative languages have evolved around \emph{sequential} machines.
-  Using such a language to describe parallel hardware therefore causes a mismatch in \emph{structue}.
-  Rather than resolving this mismatch using complex dependency analyses, we propse, in this work-in-progress-paper, a \emph{structural} approach to computations.
-  In our approach, we take as input a mathematical\todo{Functional, declarative?} description of the application, and transform it into a \emph{cyclo-static dataflow} (CSDF) graph~\cite{bilsen1996}.
+  Using such a language to describe parallel hardware therefore causes a mismatch in \emph{structure}.
+  Rather than resolving this mismatch using complex dependency analyses, we propose, in this work-in-progress-paper, a \emph{structural} approach to computations.
+  In our approach, we take as input a declarative description of the application, and transform it into a \emph{cyclo-static dataflow} (CSDF) graph~\cite{bilsen1996}.
   Transformations to enhance performance are then applied to this graph.
@@
 \begin{verbatim}
-  dotprod xs ys = 
-      fold (+) 0 (zipWith (*) xs ys)  
+dotp xs ys = fold (+) 0 (zipWith (*) xs ys)  
 \end{verbatim}
@@
   In order to determine accurate performance metrics of an application, the simulation must be accurate.
-  In SDFkit, the simulation can be used to for verify functional correctness as well as performance.
+  In SDFkit, the simulation can be used to verify functional correctness as well as performance.
   Due to a specific mapping of the application graph to hardware, a cycle accurate simulation can be performed.
@@
   The code is generated using \clash, a functional hardware description language~\cite{Baaij10}.
-  Additional to the python code that can be put in a node for simulation, \clash\ code is added for the implementation on hardware.
+  Additional to the python code in a node for simulation, \clash\ code is added for the implementation on hardware.
 
@@
 
-  Currently, SDFkit can import graphs expressed in a JSON file format.
-  These files contain a list of nodes and edges.
+  Currently, SDFkit can import graphs expressed in a JSON file containing a list of nodes and edges.
   Additionally, each node contains a python lambda expression for the functional behavior of the node during simulation.
@@
   The central widget shows a visualization of a CSDF graph which can be simulated in a step-wise fashion using the control panel on the left.
-  For debugging purposes, the data contained in each token for each simulation step is visualized in the lower widget.
+  For debugging purposes, the data in tokens is visualized in the lower widget.
 
@@
   Currently, the hardware generation backend only supports \emph{homogeneous} SDF (HSDF) graphs, which is the simplest type of SDF graph.
-  To add support for complete CSDF graphs, the edges have to support storing a variable amount of tokens each clock cycle.
-  This is in terms of hardware much more complicated.
+  To support CSDF graphs, the edges have to support storing a variable amount of tokens each clock cycle which results in more complicated hardware.
 
@@
 
-  In this paper we presented a methodology for designing hardware using a structured approach.
+  In this paper we presented a methodology and an application for designing hardware using a structured approach.
   In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a computation.
@@
   Applications are modeled using CSDF graphs which are a cycle-accurate model for the generated hardware.
-
-  As a proof of concept, an interactive simulation and hardware generation environment named SDFkit is being developed.
-  Currently, SDFkit supports visualization and simulation of HSDF, SDF and CSDF graphs.
+  This methodology is currently being implemented in SDFkit, an interactive simulation and hardware generation environment supporting visualization and simulation of CSDF graphs.
   Additionally, \clash code can be generated for HSDF graphs.

### 2016-07-07 paper/paper.tex
Last textual fixes.

@@
   Using SDFkit, CSDF graphs can be visualized and simulated in a cycle accurate manner.
-  Additionally, using the code can be generated for FPGAs.
+  Additionally, code can be generated for FPGAs.
 
@@
   First, the approach is covered in Section \ref{sec:approach} after which results are covered in Section \ref{sec:results}.
-  Finally, conclusion and future work are expressed in Section \ref{sec:conclusions}.
+  Finally, conclusions and future work are expressed in Section \ref{sec:conclusions}.
 
@@
   Since all dependencies are known, computations can be distributed over space and time by mathematical transformation rules.
-  Even though no standard C for-loops are used to express repetitive computations, this should not be a problem for programmers since similar patters are also used in map-reduce applications.
+  Even though no for-loops are used to express repetitive computations, this should not be a problem for programmers since similar patters are also used in map-reduce applications.
   Figure \ref{fig:zipwthandfoldlstruct} shows two examples of computational structures: the higher-order function \emph{zipWith} and \emph{foldl}.
@@
   That is, one may collapse a subgraph into a single node, which makes the higher-order functions explicit.
+
   \begin{figure}[h!]
@@
 
-  In order to determine accurate performance metrics of an application, the simulation must be accurate.
+  In order to determine performance metrics of an application, the simulation must be accurate.
   In SDFkit, the simulation can be used to verify functional correctness as well as performance.
@@
   This methodology is currently being implemented in SDFkit, an interactive simulation and hardware generation environment supporting visualization and simulation of CSDF graphs.
-  Additionally, \clash code can be generated for HSDF graphs.
+  Additionally, \clash\ code can be generated for HSDF graphs.
 
-  The next step in development is to extend the hardware code generation with support for SDF and CSDF graphs.
+  The next step in development is to extend the hardware code generation with support for CSDF graphs.
   Additionally, the transformations to make a tradeoff between space and time are now performed outside SDFkit.
   Integration of these transformations into SDFkit is therefore an other important step forward.
-  Finally, Interesting opportunities lie in extending the backend with a wider range of supported platform like C code and OpenCL.
+  Finally, interesting opportunities lie in extending the code generation with a wider range of supported platform like C code and OpenCL.
 

### 2016-09-12 codegen/clashcodegen.py
Removed all print statements and made sure that these are all handled by the logging class now.

@@ -8,8 +8,6 @@ author: Rinse Wester
 
 """
 
-
-from csdfgraph import *
 import re
 
 class ClashCodeGen(object):

### 2016-09-12 csdfgraph.py

@@ -12,6 +12,7 @@ import networkx as nx
 import json
 import string
 import sdfmath
+from log import Log
 from copy import deepcopy
 
 # TODO: add support for change tracking: weather file has changed -> to enable/disable save button in GUI
@@ -228,7 +229,7 @@ class CSDFGraph(nx.DiGraph):
         #  at least two nodes and one edge, proper connections
         #  and check wether all edges are connected consistenly
         #  to nodearguments and results
-        print('load file in csdfgraph: ' + filename)
+        Log.addLogMessage(Log.INFO, 'Opened grap ' + filename)
         self.filename = filename
         with open(filename, 'r') as f:
             jsonstr = f.read()
@@ -321,13 +322,10 @@ class CSDFGraph(nx.DiGraph):
         # add all edges to temporary dict in form of a list
         graphDict['edges'] = edgesList
 
-        # print(json.dumps(graphDict, sort_keys=False, indent=4))
-
         # Last but not leat, write the graph to the file
         with open(fname, 'w') as outfile:
-            json.dump(graphDict, outfile, sort_keys=False, indent=4)
-            print('Saved graph in: ' + fname)
-
+            json.dump(graphDict, outfile, sort_keys=True, indent=4)
+            Log.addLogMessage(Log.INFO, 'Saved graph ' + fname)
 
     def updateNodeFunction(self, nodename, funcstr):
         self.node[nodename]['funcstr'] = funcstr

### 2016-09-12 edge.py

@@ -8,9 +8,10 @@ author: Sander Giesselink
 
 """
 
-from PyQt5.QtWidgets import QGraphicsItem, QInputDialog
+from PyQt5.QtWidgets import QGraphicsItem, QInputDialog, QMessageBox
 from PyQt5.QtCore import Qt, QRectF, QPointF
 from PyQt5.QtGui import QColor, QPen, QBrush, QPainterPath, QFont
+from log import Log
 
 class Edge(QGraphicsItem):
 
@@ -427,11 +428,8 @@ class Edge(QGraphicsItem):
                 self.pRates = newPRates
                 self.tokenCluster.widget.editPRates(self.tokenCluster.src, self.tokenCluster.dst, newPRates)
             except:
-                print('Invalid pRate entry')
-
-            # newPRates = eval(newPRatesStr)
-            # self.pRates = newPRates
-            # self.tokenCluster.widget.editPRates(self.tokenCluster.src, self.tokenCluster.dst, newPRates)
+                Log.addLogMessage(Log.ERROR, 'Production rate not valid.')
+                QMessageBox.critical(self.tokenCluster.widget, 'Error', 'Production rate not valid.')
 
     def setCRatesActiontriggered(self):
         cRatesStr = str(self.cRates)
@@ -443,11 +441,8 @@ class Edge(QGraphicsItem):
                 self.cRates = newCRates
                 self.tokenCluster.widget.editCRates(self.tokenCluster.src, self.tokenCluster.dst, newCRates)
             except:
-                print('Invalid cRate entry')
-
-            # newCRates = eval(newCRatesStr)
-            # self.cRates = newCRates
-            # self.tokenCluster.widget.editCRates(self.tokenCluster.src, self.tokenCluster.dst, newCRates)
+                Log.addLogMessage(Log.ERROR, 'Consumption rate not valid.')
+                QMessageBox.critical(self.tokenCluster.widget, 'Error', 'Consumption rate not valid.')
 
     def calculateEdgeColors(self, color):
         #Calculate all edge colors based on a given color

### 2016-09-12 graphicsview.py

@@ -13,6 +13,7 @@ from PyQt5.QtWidgets import QWidget, QGraphicsView, QGraphicsScene, QHBoxLayout,
 from PyQt5.QtCore import Qt, QRectF, QPointF
 from PyQt5.QtGui import QTransform, QPainter, QColor
 from graph import Graph
+from log import Log
 
 class GraphicsView(QGraphicsView):
 
@@ -218,7 +219,7 @@ class GraphWidget(QWidget):
             i = i + 1
 
     def editTokens(self, src, dst, newTokens):
-        print('Update tokens between: ' + str(src) + '--->' + str(dst) + ' to: ' + str(newTokens))
+        Log.addLogMessage(Log.INFO, 'Tokens for edge ' + str((src, dst)) + ' updated to ' + str(newTokens))
         self.graphData[src][dst]['tkns'] = newTokens
         newTokens = str(newTokens)
         self.graphData.updateTokens((src, dst), newTokens)
@@ -227,27 +228,27 @@ class GraphWidget(QWidget):
         self.graphData._storestate()
         
     def editNodeFunction(self, nodeName, newFunction):
-        print('Update function to: ' + str(newFunction))
+        Log.addLogMessage(Log.INFO, 'Function of node ' + nodeName + ' updated to ' + str(newFunction))
         self.graphData.node[nodeName]['funcstr'] = newFunction
         self.graphData.updateNodeFunction(nodeName, newFunction)
 
     def editNodePosition(self, nodeName, newPos):
-        print('Node', nodeName, 'moved to:', newPos)
+        Log.addLogMessage(Log.INFO, 'Position of node ' + nodeName + ' updated to ' + str(newPos))
         self.graphData.node[nodeName]['pos'] = newPos.x(), newPos.y()
 
     def editClashCode(self, nodeName, newClashCode):
-        print('Update CLaSH code to: ' + str(newClashCode))
+        Log.addLogMessage(Log.INFO,'CLaSH code of ' + nodeName + ' updated')
         self.graphData.node[nodeName]['clashcode'] = newClashCode
         self.graphData.updateClashCode(nodeName, newClashCode)
     
     def editPRates(self, src, dst, newPRates):
-        print('Update pRates to: ' + str(newPRates))
+        Log.addLogMessage(Log.INFO, 'Production rates for edge ' + str((src, dst)) + ' updated to ' + str(newPRates))
         self.graphData[src][dst]['prates'] = newPRates
         newPRates = str(newPRates)
[…]

### 2016-09-12 mainwindow.py

@@ -2,7 +2,7 @@
 # -*- coding: utf-8 -*-
 
 """
-Widget to display simulation data of a CSDF graph.
+Mainwindow of SDFkit showing all widgets.
 
 author: Rinse Wester
 
@@ -13,14 +13,12 @@ from PyQt5.QtWidgets import QDockWidget, QApplication, QMainWindow, QAction, QFi
 from PyQt5.QtCore import Qt
 from PyQt5.QtGui import QIcon
 
-from csdfgraph import CSDFGraph
+from csdfgraph import CSDFGraph, G0
 from runwindow import RunWindow
 from logwindow import LogWidget
 from graphicsview import GraphWidget
 
-from codegen.clashcodegen import *
-from codegen.ccodegen import *
-from codegen.openclcodegen import *
+from codegen.clashcodegen import ClashCodeGen
 
 
 class MainWindow(QMainWindow):

### 2016-09-12 node.py

@@ -9,10 +9,11 @@ author: Sander Giesselink
 """
 
 import sys
-from PyQt5.QtWidgets import QWidget, QGraphicsItem, QPushButton, QVBoxLayout, QMenu, QAction, QInputDialog
+from PyQt5.QtWidgets import QWidget, QGraphicsItem, QPushButton, QVBoxLayout, QMenu, QAction, QInputDialog, QMessageBox
 from PyQt5.QtCore import QRectF, QPointF, QPoint, Qt, QVariant
 from PyQt5.QtGui import QColor, QPainter, QBrush, QPainterPath, QLinearGradient, QFont, QContextMenuEvent
 from collections import Counter
+from log import Log
 
 class Node(QGraphicsItem):
 
@@ -279,7 +280,8 @@ class Node(QGraphicsItem):
                 self.nodeFunction = newFunctionStr
                 self.widget.editNodeFunction(self.nodeName, newFunctionStr)
             except:
-                print('Invalid function entry')
+                Log.addLogMessage(Log.ERROR, 'Invalid node function')
+                QMessageBox.critical(self.widget, 'Error', 'Invalid node function')
 
     def setClashCodeActionTriggered(self):
         clashCodeStr = self.clashCode
@@ -290,9 +292,9 @@ class Node(QGraphicsItem):
                 self.clashCode = newClashCode
                 self.widget.editClashCode(self.nodeName, newClashCode)
             except:
-                print('Invalid clashcode entry')
+                Log.addLogMessage(Log.ERROR, 'Invalid CLaSH code')
+                QMessageBox.critical(self.widget, 'Error', 'Invalid CLaSH code')
             
-
     def getIOPoint(self, sideIndex, side):
     	#Gets the point from where the IO rectangle is drawn
         addWidthForRightSide = 0
@@ -301,9 +303,7 @@ class Node(QGraphicsItem):
 
         ioPoint = QPointF(addWidthForRightSide, sideIndex * (self.ioHeightDifference + self.ioHeight) + self.ioHeight / 2)
 
-        #Returns the point of a specific io
         return ioPoint
-
 
     def getIOPointForEdge(self, side, ioType):
     	#Gets the point where an edge can connect to the IO
@@ -362,8 +362,9 @@ class Node(QGraphicsItem):
             #If mouse is over IO -> return IO
             if mousePos.x() > IOPoint.x() and mousePos.x() < IOPoint.x() + self.ioWidth:
[…]

### 2016-09-12 runwindow.py

@@ -9,11 +9,8 @@ author: Rinse Wester
 """
 
 import sys
-from PyQt5.QtWidgets import QWidget, QApplication, QVBoxLayout, QHBoxLayout, QPushButton, QLabel, QScrollArea, QComboBox, QLineEdit
-
-from csdfgraph import *
-from graphicsview import GraphWidget
-
+from PyQt5.QtWidgets import QWidget, QApplication, QVBoxLayout, QHBoxLayout, QPushButton, QLabel, QComboBox, QLineEdit
+from log import Log
 
 class RunWindow(QWidget):
 
@@ -104,7 +101,8 @@ class RunWindow(QWidget):
                 self.graphWidget.updateTokensGraph()
                 n += 1
             if n == MAX_ITERATIONS:
-                print('Condition never met')
+                Log.addLogMessage(Log.CRITICAL, 'Stop condition never met')
+
 
         self.lblStateNr.setText('State: ' + str(self.graph.stateCount() - 1))
         self.btnBack.setEnabled(self.graph.stateCount() > 1)

### 2016-09-12 tokenCluster.py

@@ -9,9 +9,10 @@ author: Sander Giesselink
 """
 
 import sys
-from PyQt5.QtWidgets import QGraphicsItem, QMenu, QAction, QInputDialog
+from PyQt5.QtWidgets import QGraphicsItem, QMenu, QAction, QInputDialog, QMessageBox
 from PyQt5.QtCore import Qt, QPoint, QPointF, QRectF
 from PyQt5.QtGui import QColor, QPainter, QPen, QBrush, QPainterPath, QFont, QContextMenuEvent, QCursor
+from log import Log
 
 class TokenCluster(QGraphicsItem):
 
@@ -70,26 +71,23 @@ class TokenCluster(QGraphicsItem):
         self.lod = option.levelOfDetailFromTransform(painter.worldTransform())
 
         if self.lod > 0.15 and self.tokensAreClusterd:
-            painter.setPen(QColor(0, 0, 0))
+            painter.setPen(Qt.black)
             painter.setBrush(self.clusterColor)
-            
-            rect = self.getClusterRect()
-            smallRect1 = QRectF(-self.clusterWidth * 0.5, -self.clusterHeight * 0.25, self.clusterWidth * 0.5, self.clusterHeight * 0.5)
-            smallRect2 = QRectF(-self.clusterWidth * 0.25, 0, self.clusterWidth * 0.5, self.clusterHeight * 0.5)
-            smallRect3 = QRectF(-self.clusterWidth * 0.25, -self.clusterHeight * 0.5, self.clusterWidth * 0.5, self.clusterHeight * 0.5)
-            smallRect4 = QRectF(0, -self.clusterHeight * 0.25, self.clusterWidth * 0.5, self.clusterHeight * 0.5)
 
+            #Make token larger when the mouse hovers over it
             if self.hover:
-            	#Make token larger when the mouse hovers over it
                 rect = self.getClusterRectHover()
-                #smallRect = QRectF(-self.clusterWidth * 0.375, -self.clusterHeight * 0.375, self.clusterWidth * 0.75, self.clusterHeight * 0.75)
                 smallRect1 = QRectF(-self.clusterWidth * 0.75, -self.clusterHeight * 0.375, self.clusterWidth * 0.75, self.clusterHeight * 0.75)
                 smallRect2 = QRectF(-self.clusterWidth * 0.375, 0, self.clusterWidth * 0.875, self.clusterHeight * 0.75)
[…]

### 2016-09-13 mainwindow.py
Renamed logwidget to signal widget.

@@ -15,7 +15,7 @@ from PyQt5.QtGui import QIcon
 
 from csdfgraph import CSDFGraph, G0
 from runwindow import RunWindow
-from logwindow import LogWidget
+from signalwindow import SignalWidget
 from graphicsview import GraphWidget
 
 from codegen.clashcodegen import ClashCodeGen
@@ -100,14 +100,14 @@ class MainWindow(QMainWindow):
         self.dwRunWindow.setWidget(self.runWindow)
         self.addDockWidget(Qt.LeftDockWidgetArea, self.dwRunWindow)
 
-        self.dwLogWindow = QDockWidget('Edge log', self)
-        self.logWindow = LogWidget()
-        self.logWindow.setMinimumHeight(250)
-        self._updateLogWindow()
-        self.dwLogWindow.setAllowedAreas(Qt.BottomDockWidgetArea)
-        self.dwLogWindow.setWidget(self.logWindow)
-        self.addDockWidget(Qt.BottomDockWidgetArea, self.dwLogWindow)
-        self.runWindow.setLogWidget(self.logWindow)
+        self.dwSignalWindow = QDockWidget('Edge log', self)
+        self.signalWindow = SignalWidget()
+        self.signalWindow.setMinimumHeight(250)
+        self._updateSignalWindow()
+        self.dwSignalWindow.setAllowedAreas(Qt.BottomDockWidgetArea)
+        self.dwSignalWindow.setWidget(self.signalWindow)
+        self.addDockWidget(Qt.BottomDockWidgetArea, self.dwSignalWindow)
+        self.runWindow.setSignalWidget(self.signalWindow)
 
         self.runWindow.setGraphWidget(self.graphWidget)
         self.setCentralWidget(self.graphWidget)
@@ -116,7 +116,7 @@ class MainWindow(QMainWindow):
         self.setGeometry(0, 30, 1300, 750)
         self.show()
 
-    def _updateLogWindow(self):
+    def _updateSignalWindow(self):
 
         edgeNames = []
         edgeData = []
@@ -124,8 +124,8 @@ class MainWindow(QMainWindow):
             for (src, dst), edata in self.graph.edgestates.items():
                 edgeNames.append(src + ' → ' + dst)
                 edgeData.append(edata)
-        self.logWindow.setEdgeLabels(edgeNames)
-        self.logWindow.setEdgeData(edgeData)
+        self.signalWindow.setEdgeLabels(edgeNames)
[…]

### 2016-09-13 runwindow.py

@@ -113,15 +113,15 @@ class RunWindow(QWidget):
         self.graphWidget.updateTokensGraph()
 
         # update the log window such that all tokens of all states are shown
-        self.lwid.setEdgeData(list(self.graph.edgestates.values()))
+        self.swid.setEdgeData(list(self.graph.edgestates.values()))
 
     def setGraphWidget(self, gwid):
 
         self.gwid = gwid
 
-    def setLogWidget(self, lwid):
+    def setSignalWidget(self, swid):
 
-        self.lwid = lwid
+        self.swid = swid
 
     def setGraph(self, graph):
 

### 2016-09-13 signalwindow.py

@@ -20,7 +20,7 @@ from PyQt5.QtGui import QPainter, QFont, QColor, QPen, QBrush, QPainterPath, QPo
 from csdfgraph import *
 
 
-class LogWidget(QWidget):
+class SignalWidget(QWidget):
     NODE_RADIUS = 20
     EDGE_DIST = 26
     EDGE_HEAD_LEN = 32

### 2016-09-13 log.py
Initial version of LogWidget class.

@@ -18,6 +18,8 @@ class Log(object):
 	WARNING = 2
 	INFO = 1
 
+	_newMessageCallback = None
+
 	_msg_list = []
 
 	def addLogMessage(msgtype, msgtext):
@@ -28,6 +30,12 @@ class Log(object):
 
 		msgtext contains the actual info message and should be human readable."""
 		Log._msg_list.append((dt.datetime.now(), msgtype, msgtext))
+
+		if Log._newMessageCallback is not None:
+			Log._newMessageCallback(msgtype, msgtext)
+
+	def setNewMessageCallBack(cbfunc):
+		Log._newMessageCallback = cbfunc
 
 	def getLogMessages(mintype=INFO):
 		"""Get all recorded logmessages

### 2016-09-13 logwidget.py

@@ -1,0 +1,73 @@
+#!/usr/bin/python3
+# -*- coding: utf-8 -*-
+
+"""
+Widget to display log messages.
+
+author: Rinse Wester
+
+"""
+
+import sys
+from PyQt5.QtWidgets import QWidget, QApplication, QVBoxLayout, QHBoxLayout, QPushButton, QListWidget
+from log import Log
+import random as rdm 
+
+class LogWidget(QWidget):
+
+    def __init__(self):
+        super().__init__()
+
+        self.initUI()
+
+        self.show()
+
+    def initUI(self):
+
+        self.btnclear = QPushButton("Clear messages", self)
+        self.btnclear.clicked.connect(self._clearClicked)
+
+        self.btnAddM = QPushButton("Add message", self)
+        self.btnAddM.clicked.connect(self._addMClicked)
+        
+        self.lwmessages = QListWidget(self)
+        for _, msgtype, msgtext in Log.getLogMessages():
+            self.addLogItem(tp, msg)
+
+        self.hboxlayout = QHBoxLayout()
+        self.hboxlayout.addWidget(self.btnclear)
+        self.hboxlayout.addStretch()
+        self.hboxlayout.addWidget(self.btnAddM)
+
+        self.vboxlayout = QVBoxLayout()
+        self.vboxlayout.addLayout(self.hboxlayout)
+        self.vboxlayout.addWidget(self.lwmessages)
+
+        self.setLayout(self.vboxlayout)
+
+        # Make sure this widget listens to new logevents
+        Log.setNewMessageCallBack(self._newMessageAddedToLog)
+
+    def _clearClicked(self):
+        self.lwmessages.clear()
+        Log.clearMessages()
+
+    def _addMClicked(self):
+        msgtype = rdm.choice([Log.INFO, Log.WARNING, Log.CRITICAL, Log.ERROR])
+        msgtext = 'message ... ' + rdm.choice('ABCDEFGHI')
+        Log.addLogMessage(msgtype, msgtext)
+
+    def _newMessageAddedToLog(self, msgtype, msgtext):
+        self.addLogItem(msgtype, msgtext)
+
+    def addLogItem(self, msgtype, msgtext):
+        self.lwmessages.addItem(str(msgtype) + ' > ' + msgtext)
+
+
+if __name__ == '__main__':
+
+    app = QApplication(sys.argv)
+    ex = LogWidget()
+    app.exec_()
+    app.deleteLater()
+    sys.exit()

### 2016-09-13 log.py
Removed the critical type from the log class and the rest of SDFkit.

@@ -13,8 +13,7 @@ import datetime as dt
 class Log(object):
 	"""Log class to store logmessages from SDFkit"""
 
-	ERROR = 4
-	CRITICAL = 3
+	ERROR = 3
 	WARNING = 2
 	INFO = 1
 
@@ -25,8 +24,8 @@ class Log(object):
 	def addLogMessage(msgtype, msgtext):
 		"""Add a message to the list of log messages
 
-		msgtype is the type of message and must be one of: Log.ERROR, Log.CRITICAL,
-		Log.WARNING, Log.INFO.
+		msgtype is the type of message and must be one of: Log.ERROR, Log.WARNING,
+		Log.INFO.
 
 		msgtext contains the actual info message and should be human readable."""
 		Log._msg_list.append((dt.datetime.now(), msgtype, msgtext))
@@ -41,7 +40,7 @@ class Log(object):
 		"""Get all recorded logmessages
 
 		When mintype is given, only message with a minimum severity are returned.
-		For example when mintype = CRITICAL, only CRITICAL and ERROR messages are given.
+		For example when mintype = WARNING, only WARNING and ERROR messages are given.
 		Similarly, when mintype = INFO, all messages are returned"""
 		return list(filter(lambda tpl: tpl[1] >= mintype, Log._msg_list))
 

### 2016-09-13 logwidget.py

@@ -53,7 +53,7 @@ class LogWidget(QWidget):
         Log.clearMessages()
 
     def _addMClicked(self):
-        msgtype = rdm.choice([Log.INFO, Log.WARNING, Log.CRITICAL, Log.ERROR])
+        msgtype = rdm.choice([Log.INFO, Log.WARNING, Log.ERROR])
         msgtext = 'message ... ' + rdm.choice('ABCDEFGHI')
         Log.addLogMessage(msgtype, msgtext)
 

### 2016-09-13 runwindow.py

@@ -101,7 +101,7 @@ class RunWindow(QWidget):
                 self.graphWidget.updateTokensGraph()
                 n += 1
             if n == MAX_ITERATIONS:
-                Log.addLogMessage(Log.CRITICAL, 'Stop condition never met')
+                Log.addLogMessage(Log.WARNING, 'Stop condition never met')
 
 
         self.lblStateNr.setText('State: ' + str(self.graph.stateCount() - 1))

### 2016-09-13 logwidget.py
Added icons to the logwidget.

@@ -9,7 +9,8 @@ author: Rinse Wester
 """
 
 import sys
-from PyQt5.QtWidgets import QWidget, QApplication, QVBoxLayout, QHBoxLayout, QPushButton, QListWidget
+from PyQt5.QtWidgets import QWidget, QApplication, QVBoxLayout, QHBoxLayout, QPushButton, QListWidget, QListWidgetItem
+from PyQt5.QtGui import QIcon
 from log import Log
 import random as rdm 
 
@@ -61,7 +62,14 @@ class LogWidget(QWidget):
         self.addLogItem(msgtype, msgtext)
 
     def addLogItem(self, msgtype, msgtext):
-        self.lwmessages.addItem(str(msgtype) + ' > ' + msgtext)
+        if msgtype == Log.INFO:
+            icon = QIcon('images/information.png')
+        elif msgtype == Log.WARNING:
+            icon = QIcon('images/warning.png')
+        else:
+            icon = QIcon('images/error.png')
+        item = QListWidgetItem(icon, msgtext)
+        self.lwmessages.addItem(item)
 
 
 if __name__ == '__main__':

### 2016-09-13 log.py
Added function to determine type of last message.

@@ -44,6 +44,17 @@ class Log(object):
 		Similarly, when mintype = INFO, all messages are returned"""
 		return list(filter(lambda tpl: tpl[1] >= mintype, Log._msg_list))
 
+	def messageCount():
+		"""returns the number of messages in the log."""
+		return len(Log._msg_list)
+
+	def lastMessageType():
+		"""returns the type of the last message"""
+		if Log.messageCount() > 0:
+			return Log._msg_list[-1][1]
+		else:
+			return None
+
 	def clearMessages():
 		"""Remove all logmessages."""
 		Log._msg_list.clear()

### 2016-09-13 mainwindow.py

@@ -100,7 +100,7 @@ class MainWindow(QMainWindow):
         self.dwRunWindow.setWidget(self.runWindow)
         self.addDockWidget(Qt.LeftDockWidgetArea, self.dwRunWindow)
 
-        self.dwSignalWindow = QDockWidget('Edge log', self)
+        self.dwSignalWindow = QDockWidget('Edge signals', self)
         self.signalWindow = SignalWidget()
         self.signalWindow.setMinimumHeight(250)
         self._updateSignalWindow()

### 2016-09-14 logwidget.py
Added log window as dockwidget.

@@ -33,7 +33,7 @@ class LogWidget(QWidget):
         
         self.lwmessages = QListWidget(self)
         for _, msgtype, msgtext in Log.getLogMessages():
-            self.addLogItem(tp, msg)
+            self.addLogItem(msgtype, msgtext)
 
         self.hboxlayout = QHBoxLayout()
         self.hboxlayout.addWidget(self.btnclear)

### 2016-09-14 mainwindow.py

@@ -15,6 +15,7 @@ from PyQt5.QtGui import QIcon
 
 from csdfgraph import CSDFGraph, G0
 from runwindow import RunWindow
+from logwidget import LogWidget
 from signalwindow import SignalWidget
 from graphicsview import GraphWidget
 
@@ -108,6 +109,12 @@ class MainWindow(QMainWindow):
         self.dwSignalWindow.setWidget(self.signalWindow)
         self.addDockWidget(Qt.BottomDockWidgetArea, self.dwSignalWindow)
         self.runWindow.setSignalWidget(self.signalWindow)
+
+        self.dwLogWindow = QDockWidget('Log', self)
+        self.logWindow = LogWidget()
+        self.dwLogWindow.setAllowedAreas(Qt.BottomDockWidgetArea)
+        self.dwLogWindow.setWidget(self.logWindow)
+        self.addDockWidget(Qt.BottomDockWidgetArea, self.dwLogWindow)
 
         self.runWindow.setGraphWidget(self.graphWidget)
         self.setCentralWidget(self.graphWidget)

### 2016-09-14 logwidget.py
Removed testing button from logwidget.

@@ -12,7 +12,6 @@ import sys
 from PyQt5.QtWidgets import QWidget, QApplication, QVBoxLayout, QHBoxLayout, QPushButton, QListWidget, QListWidgetItem
 from PyQt5.QtGui import QIcon
 from log import Log
-import random as rdm 
 
 class LogWidget(QWidget):
 
@@ -27,9 +26,6 @@ class LogWidget(QWidget):
 
         self.btnclear = QPushButton("Clear messages", self)
         self.btnclear.clicked.connect(self._clearClicked)
-
-        self.btnAddM = QPushButton("Add message", self)
-        self.btnAddM.clicked.connect(self._addMClicked)
         
         self.lwmessages = QListWidget(self)
         for _, msgtype, msgtext in Log.getLogMessages():
@@ -38,7 +34,6 @@ class LogWidget(QWidget):
         self.hboxlayout = QHBoxLayout()
         self.hboxlayout.addWidget(self.btnclear)
         self.hboxlayout.addStretch()
-        self.hboxlayout.addWidget(self.btnAddM)
 
         self.vboxlayout = QVBoxLayout()
         self.vboxlayout.addLayout(self.hboxlayout)
@@ -52,11 +47,6 @@ class LogWidget(QWidget):
     def _clearClicked(self):
         self.lwmessages.clear()
         Log.clearMessages()
-
-    def _addMClicked(self):
-        msgtype = rdm.choice([Log.INFO, Log.WARNING, Log.ERROR])
-        msgtext = 'message ... ' + rdm.choice('ABCDEFGHI')
-        Log.addLogMessage(msgtype, msgtext)
 
     def _newMessageAddedToLog(self, msgtype, msgtext):
         self.addLogItem(msgtype, msgtext)

### 2016-09-14 mainwindow.py
Moved both the signal and logdockwidget into a tabbed view.

@@ -116,6 +116,8 @@ class MainWindow(QMainWindow):
         self.dwLogWindow.setWidget(self.logWindow)
         self.addDockWidget(Qt.BottomDockWidgetArea, self.dwLogWindow)
 
+        self.tabifyDockWidget(self.dwLogWindow, self.dwSignalWindow)
+
         self.runWindow.setGraphWidget(self.graphWidget)
         self.setCentralWidget(self.graphWidget)
 

### 2016-09-14 mainwindow.py
ADded popup to indicate that hardware generation is completed.

@@ -161,6 +161,7 @@ class MainWindow(QMainWindow):
     def clashcodegenActionTriggered(self):
         try:
             ClashCodeGen.generateCode(self.graph, './output/' + self.graph.name)
+            QMessageBox.information(self, 'CLaSH code generation', 'CLaSH code generation completed')
         except Exception as e:
             QMessageBox.critical(
                 self, 'Generate CLaSH code',

### 2016-09-14 graphicsview.py
removed the loggin of node position changes.

@@ -20,6 +20,7 @@ class GraphicsView(QGraphicsView):
     def __init__(self, widget):
         super().__init__()
         self.widget = widget
+        
         # Remove ugly one pixel border by changing the framestyle
         self.setFrameStyle(QFrame.NoFrame); 
 
@@ -233,7 +234,7 @@ class GraphWidget(QWidget):
         self.graphData.updateNodeFunction(nodeName, newFunction)
 
     def editNodePosition(self, nodeName, newPos):
-        Log.addLogMessage(Log.INFO, 'Position of node ' + nodeName + ' updated to ' + str(newPos))
+        # Log.addLogMessage(Log.INFO, 'Position of node ' + nodeName + ' updated to ' + str(newPos))
         self.graphData.node[nodeName]['pos'] = newPos.x(), newPos.y()
 
     def editClashCode(self, nodeName, newClashCode):

### 2016-09-14 codegen/clashcodegen.py
Added clash code to distinct outputs example. simulation works in CLaSH.

@@ -9,6 +9,7 @@ author: Rinse Wester
 """
 
 import re
+from log import Log
 
 class ClashCodeGen(object):
     """docstring for ClashCodeGen"""
@@ -56,7 +57,7 @@ class ClashCodeGen(object):
             filename = graph.name.lower() + '.hs'
             with open('codegen/clash_code/' + filename, 'w') as f:
                 f.write(templatestr)
-                print('Generating CLaSH code in ', filename)
+                Log.addLogMessage( Log.INFO, 'CLaSH code generated in ' + filename)
 
     def _getEdgeTypes(graph):
         edgeTypes = {}

### 2016-09-14 signalwindow.py

@@ -13,11 +13,9 @@ author: Rinse Wester
 # scrollview stays too wide
 
 import sys
-from PyQt5.QtWidgets import QWidget, QDockWidget, QApplication, QLayout, QVBoxLayout, QHBoxLayout, QLabel, QScrollArea
+from PyQt5.QtWidgets import QWidget, QLayout, QVBoxLayout, QHBoxLayout, QLabel, QScrollArea
 from PyQt5.QtCore import Qt, QRect, QPoint
-from PyQt5.QtGui import QPainter, QFont, QColor, QPen, QBrush, QPainterPath, QPolygon, QPalette
-
-from csdfgraph import *
+from PyQt5.QtGui import QPainter, QFont, QPen, QBrush, QPolygon
 
 
 class SignalWidget(QWidget):

### 2016-09-15 paper/csdf-dp.tex
Still had the commit the last version of the paper as presented at the FSP16 workshop in Lausanne.

@@
 
-\tikzstyle{sdfgnode} = [circle,draw=black,draw opacity=0.7,fill=yellow!30,fill opacity=0.9,inner sep=0,minimum width=14pt,font=\scriptsize,text=black,text opacity=1]%
-\tikzstyle{sdfgdata} = [sdfgnode, inner sep=1pt,fill=blue!60!black,fill opacity=0.4]%
-\tikzstyle{sdfgmem} = [sdfgnode, rectangle, rounded corners=4pt, inner sep=2pt,fill=blue!60!black,fill opacity=0.1]%
+\tikzstyle{sdfgnode} = [circle,draw=black,fill=white,,inner sep=0,minimum width=14pt,font=\scriptsize,text=black,text opacity=1]%
+\tikzstyle{sdfgdata} = [sdfgnode, inner sep=1pt,fill=white]%
+\tikzstyle{sdfgmem} = [sdfgnode, rectangle, rounded corners=4pt, inner sep=2pt,fill=white]%
 \tikzstyle{sdfgarc} = [->,minimum width=1pt,>=latex,sloped]%

### 2016-09-15 paper/paper_final.tex
Still had the commit the last version of the paper as presented at the FSP16 workshop in Lausanne.

--- 2016-07-07 paper/paper.tex
@@
-\documentclass[journal]{IEEEtran}
-\usepackage{blindtext}
+\makeatletter
+\makeatother\documentclass[10pt,english,oneside,twocolumn,a4paper]{article}% change 'a4paper' to 'letter' to use imperial paper format.
 \usepackage{graphicx}
+%% Font: Times
+\usepackage[utf8]{inputenc}
+\usepackage{mathptmx}
+%\def\rmdefault{utm}
+\usepackage{tabularx}
+\usepackage{ragged2e}
 \usepackage{todonotes}
-\usepackage{cite}
-\usepackage[cmex10]{amsmath}
+\usepackage{flushend}
+\usepackage[singlelinecheck=false]{caption}
+\usepackage[T1]{fontenc}
+\usepackage[numbers]{natbib}
+\usepackage{amsmath}
+\usepackage{babel}
 \usetikzlibrary{calc,positioning}
@@
 
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
+\pagestyle{empty}
+\hoffset-1in
+\voffset-1in
+\oddsidemargin20truemm
+\makeatletter
+\let\ps@plain\ps@empty
+\def\@xivpt{14pt}
+\raggedbottom
+\setcounter{secnumdepth}{4}
+\columnsep5mm
+\def\@sect#1#2#3#4#5#6[#7]#8{%
+  \ifnum #2<2
+    \null\par\vskip-15pt
+  \fi
+  \ifnum #2>\c@secnumdepth 
+    \let\@svsec\@empty
+  \else
+    \refstepcounter{#1}%
+    \protected@edef\@svsec{%
+      \ifnum #2<4
+        \hb@xt@10mm{\csname the#1\endcsname}\relax
+      \else
+        \hb@xt@12mm{\csname the#1\endcsname}\relax
+      \fi}%
+  \fi
+  \@tempskipa #5\relax
+  \ifdim \@tempskipa>\z@
+    \begingroup
+      #6{%
+        \@hangfrom{\hskip #3\relax\@svsec}%
+          \interlinepenalty \@M #8\@@par}%
+    \endgroup
+    \csname #1mark\endcsname{#7}%
+    \addcontentsline{toc}{#1}{%
+      \ifnum #2>\c@secnumdepth \else  
+        \protect\numberline{\csname the#1\endcsname}%
+      \fi 
+      #7}%
+  \else
+    \def\@svsechd{%
+      #6{\hskip #3\relax
+      \@svsec #8}%
+      \csname #1mark\endcsname{#7}%
+      \addcontentsline{toc}{#1}{%
+        \ifnum #2>\c@secnumdepth \else
+          \protect\numberline{\csname the#1\endcsname}%
+        \fi
+        #7}}%
+  \fi
+  \@xsect{#5}}%
+\renewcommand\LARGE{\@setfontsize\LARGE{16}{20}}
+\renewcommand\abstract[2][Abstract]{\def\heading@abstract{#1}\def\@abstract{#2}}
+\def\affil#1{\def\@affil{#1}}
+%% Def. Titelei
+\headheight0pt
+\headsep0mm
+\topskip10pt
+\topmargin23mm
+\textwidth170mm
+\textheight58\baselineskip
+\def\@maketitle{%
+  \newpage
+  \null
+  \let \footnote \thanks
+    {\addvspace{-5pt}\LARGE\bfseries\RaggedRight \@title \par}%
+    \vskip 5.75mm%
+    {\fontsize{12}{14}\selectfont
+      % \lineskip 1ex%
+      \@author,\space\@affil}%
+    \vskip 15.75mm%
+    {{\Large\bfseries\RaggedRight\heading@abstract}\par\vskip14pt
+      \@abstract}%
+  \par
+  \vskip 4\baselineskip}
 
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
+\renewcommand\section{\@startsection {section}{1}{\z@}%
+                                   {-18pt}%
+                                   {6pt}%
+                                   {\Large\bfseries\RaggedRight}}
+\renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
+                                     {10pt \@plus 1ex \@minus .2ex}%
+                                     {2.5pt}%
+                                     {\normalfont\large\bfseries\RaggedRight}}
+\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\z@}%
+                                     {12pt}%
+                                     {3pt}%
+                                     {\normalsize\bfseries\RaggedRight}}
+\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
+                                    {11pt}%
+                                    {3pt}%
+                                    {\normalfont\normalsize\RaggedRight}}
+\renewcommand\subparagraph{\@startsection{subparagraph}{5}{\parindent}%
+                                       {3.25ex \@plus1ex \@minus .2ex}%
+                                       {-1em}%
+                                      {\normalfont\normalsize\bfseries\RaggedRight}}
+\parindent\p@
+\parskip\z@
+\bibsep1pt
+\setlength\bibhang\bibindent
+\DeclareCaptionLabelSeparator{enskip}{\enskip}
+\captionsetup{labelsep=enskip,justification=RaggedRight,labelfont=bf,skip=14pt,belowskip=2pt}
+\renewcommand\bibsection{\section{Literature}}
+\makeatother
 
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
+%%%%
+%%%% Insert custom content below this line
+%%%% --------------------------------------------------
 
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
+\title{An interactive environment for mapping computational structures to FPGAs}
 
-% *** SUBFIGURE PACKAGES ***
-%\usepackage[tight,footnotesize]{subfigure}
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
+\author{Rinse~Wester~and~Robert~de~Groote}
+\affil{\\Computer Architecture for Embedded Systems,\\University of Twente\\ \{r.wester, robert.degroote\}@utwente.nl}
 
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
-% This package may be useful when used in conjunction with IEEEtran.cls'
-% captionsoff option. Some IEEE journals/societies require that submissions
-% have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.3.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% For subfigure.sty:
-% \let\MYorigsubfigure\subfigure
-% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat/subfig command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-\title{An interactive environment for mapping computational structures to FPGAs}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-
-\author{Rinse~Wester~and~Robert~de~Groote \\CAES group, EEMCS\\ University of Twente\\ \{r.wester, robert.degroote\}@utwente.nl}
-
-% make the title area
-\maketitle
-
-\begin{abstract}
-  In this paper we propose a methodology to translate computational structures to hardware.
+\abstract[Abstract]{In this paper we propose a methodology to translate computational structures to hardware.
   Computational structures express both the computation and the ordering of computations.
@@
   As a proof of concept, SDFkit is developed.
-  SDFkit is a cycle accurate simulation environment for these computational structures and has a backend to generate FPGA code.
-\end{abstract}
+  SDFkit is a cycle accurate simulation and development environment for these computational structures.
+  Additionally, SDFkit has a code generation backend to generate FPGA code.}
 
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-  Structure, Computations, FPGA, SDFkit
-\end{IEEEkeywords}
+\begin{document}
 
-\IEEEpeerreviewmaketitle
+\maketitle
 
@@
   Rather than resolving this mismatch using complex dependency analyses, we propose, in this work-in-progress-paper, a \emph{structural} approach to computations.
-  In our approach, we take as input a declarative description of the application, and transform it into a \emph{cyclo-static dataflow} (CSDF) graph~\cite{bilsen1996}.
+
+  In our approach, we take as input a declarative description of the application where iteration is expressed using computational structures.
+  These structures represent a template of how computations depend on each other without enforcing ordering in time.
+  This description is then transformed into a \emph{cyclo-static dataflow} (CSDF) graph~\cite{bilsen1996}.
   Transformations to enhance performance are then applied to this graph.
@@
 
-  As a proof of concept to show the effectiveness of the approach, an interactive environment for simulation and hardware generation  is being developed named SDFkit.
-  Using SDFkit, CSDF graphs can be visualized and simulated in a cycle accurate manner.
+  As a proof of concept to show the effectiveness of the approach, SDFkit is being developed.
+  SDFkit is an interactive environment for simulation and FPGA code generation.
+  Using SDFkit, CSDF graphs can be visualized, modified and simulated to verify functionality and to evaluate performance after applying transformations.
   Additionally, code can be generated for FPGAs.
@@
 
-  Computational structures are borrowed from functional programming languages so called higher-order functions.
+  Figure~\ref{fig:approach} shows a graphical representation of the approach to hardware design.
+  From left to right, the method starts out with a specification of the program in a simple functional language.
+  This specification is parsed and translated into a graph which becomes the intermediate representation of the program.
+  All transformations and optimizations are applied to the graph resulting in a new graph.
+  The final step is the code generation step.
+  During this step target-specific code is generated based on the graph resulting in hardware description code (VHDL) or software (C).
+  Note that different targets require different transformations for the intermediate graph in order to optimize performance.
+
+  \begin{figure}[h!]
+    \centering
+    \input{steps}
+    \caption{Approach to hardware design}
+    \label{fig:approach}
+  \end{figure}
+
+  The computational structures used in the program  specification are borrowed from functional programming languages.
+  In functional programming languages like Haskell, these are called higher-order functions.
+  A higher-order function can accept functions as argument instead of just values.
   These functions are very suitable to express the structure in computations and therefore a good source of parallelism~\cite{Wester15}.
@@
   Since all dependencies are known, computations can be distributed over space and time by mathematical transformation rules.
-  Even though no for-loops are used to express repetitive computations, this should not be a problem for programmers since similar patters are also used in map-reduce applications.
+  Even though no for-loops are used to express repetitive computations, this should not be a problem for programmers since similar patters are also used in map-reduce frameworks like Hadoop~\cite{shvachko2010}.
   Figure \ref{fig:zipwthandfoldlstruct} shows two examples of computational structures: the higher-order function \emph{zipWith} and \emph{foldl}.
@@
 
+  SDFkit is under active development and is gaining a lot of features.
+  Currently, the simulation environment is extended to support hierarchical graphs for a higher level of abstraction.
+  For usability, the visualization of the graph and debug capabilities are extended.
+
   Currently, SDFkit can import graphs expressed in a JSON file containing a list of nodes and edges.
@@
   After opening, both the functionality of the nodes and data on the edges can be altered using the GUI.
-
   Figure \ref{fig:screenshot} shows a screenshot of SDFkit.
-  The central widget shows a visualization of a CSDF graph which can be simulated in a step-wise fashion using the control panel on the left.
-  For debugging purposes, the data in tokens is visualized in the lower widget.
 
@@
     \centering
-    \includegraphics[width=3in]{screenshot.png}
+    \includegraphics[width=80mm]{screenshot.png}
     \caption{Screenshot of SDFkit}
@@
 
+  The central widget shows a visualization of a CSDF graph which can be simulated in a step-wise fashion using the control panel on the left.
+  For debugging purposes, the data in tokens is visualized in the lower widget.
+
   Currently, the hardware generation backend only supports \emph{homogeneous} SDF (HSDF) graphs, which is the simplest type of SDF graph.
+  The resulting generated hardware has been verified using simulation and shows the same behavior as the simulation of the HSDF graph.
   To support CSDF graphs, the edges have to support storing a variable amount of tokens each clock cycle which results in more complicated hardware.
+  A stand-alone graph using a CSDF edge has been implemented and produces correct simulation results.
+  Instantiation of the edges and nodes still has to be automated to complete the hardware generation for CSDF graphs.
 
@@
 
-  The next step in development is to extend the hardware code generation with support for CSDF graphs.
-  Additionally, the transformations to make a tradeoff between space and time are now performed outside SDFkit.
-  Integration of these transformations into SDFkit is therefore an other important step forward.
-  Finally, interesting opportunities lie in extending the code generation with a wider range of supported platform like C code and OpenCL.
+  Currently, the hardware code generation back-end is extended to support CSDF graphs.
+  Additionally, the generation of a graph and transformations applied to these graph are performed in a tool outside SDFkit.
+  Integration of this tool into SDFkit is therefore an other important step forward.
+  Finally, interesting opportunities lie in extending the code generation with a wider range of supported platforms like C code and OpenCL.
 
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-% \begin{thebibliography}{1}
-
-% \bibitem{IEEEhowto:kopka}
-% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-%   \bibliographystyle{unsrt}
-% {\small\bibliography{biblio}}
-
+%%% Please leave the following line as is and insert your bibliography items below.
+% \begin{thebibliography}{9}\leftskip1mm\advance\labelsep\leftskip
+% \bibitem{citation:1} Analog Devices: Analog Design Seminar, Munich: Analog Devices GmbH, 1989
+% \bibitem{citation:2} Lancaster, Don: Das Aktiv-Filter-Kochbuch, Va- terstetten: IWT, 1986
+% \bibitem{citation:3} Grütz, A.: Jahrbuch Elektrotechnik ’98,: VDE-VER- LAG, Berlin, Offenbach 1997
+% \bibitem{citation:4} Huneus, H.: Lex, A.: Magnetische Eigenschaft von nichtkornorientiertem Elektroblech. etz Elektrotech.  Z. 112 (1991) H. 22, S. 1204-1208
+% \bibitem{citation:5} Abramowitz, M.: Handbook of mathematical func- tions, 3rd ed., New York: Dover, 1980
+% \bibitem{citation:6} Guidelines for ETEP Authors, ETEP European Transactions on Electrical Power. Vol. 7, No. 5, Sept./Oct. 1997, pp. 363-364
 % \end{thebibliography}
-
-% bibliography{IEEEabrv,biblio}
 
@@
 
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
 \end{document}

### 2016-09-15 paper/steps.tex
Still had the commit the last version of the paper as presented at the FSP16 workshop in Lausanne.

\begin{tikzpicture}[xscale=0.7]

\tikzstyle{state} = [rectangle, draw=black,fill=white,rounded corners=1mm, inner sep=2mm,minimum width=14pt,font=\scriptsize,text=black]

\tikzstyle{sdfgnode} = [circle,draw=black,fill=white,inner sep=0,minimum width=14pt,font=\scriptsize,text=black]%
\tikzstyle{sdfgdata} = [sdfgnode, inner sep=1pt,fill=white]%
\tikzstyle{sdfgmem} = [sdfgnode, rectangle, rounded corners=4pt, inner sep=2pt,fill=white]%
\tikzstyle{sdfgarc} = [->,minimum width=2pt,>=latex,sloped]%

\node[state] (inplang) at (0,0) {Specification};
\node[state] (csdfgraph) at (5,0) {CSDF graph};
\node[state] (hardware) at (10,1) {Hardware};
\node[state] (software) at (10,-1) {Software};

\draw[sdfgarc] (inplang) -- node[above, font=\scriptsize] {Parsing} (csdfgraph);
\draw[sdfgarc] (csdfgraph) -- node[above, font=\scriptsize] {Code gen.} (hardware);
\draw[sdfgarc] (csdfgraph) -- node[above, font=\scriptsize] {Code gen.} (software);

\draw[sdfgarc] (csdfgraph)
    .. controls ($(csdfgraph) + (-50:1)$) and ($(csdfgraph) + (0.5,-1)$) .. ($(csdfgraph) + (0, -1)$)
    node[below, font=\scriptsize] {Transformations}
    .. controls ($(csdfgraph) + (-0.5,-1)$) and ($(csdfgraph) + (-130:1)$) ..
    (csdfgraph);

\end{tikzpicture}

### 2016-09-15 signalwindow.py
Inital version of new signalwidget: based on QTableWidget with better scrolling then previous one and movable rows.

@@ -8,20 +8,13 @@ author: Rinse Wester
 
 """
 
-# TODO add a cucle number bar on top
-# TODO fix resize issue after resetting graph, i.e., inner widget of
-# scrollview stays too wide
-
-import sys
-from PyQt5.QtWidgets import QWidget, QLayout, QVBoxLayout, QHBoxLayout, QLabel, QScrollArea
+from PyQt5.QtWidgets import QApplication, QWidget, QLayout, QVBoxLayout, QHBoxLayout, QLabel, QScrollArea, QTableWidget, QAbstractItemView, QHeaderView, QPushButton
 from PyQt5.QtCore import Qt, QRect, QPoint
 from PyQt5.QtGui import QPainter, QFont, QPen, QBrush, QPolygon
+import sys
 
 
 class SignalWidget(QWidget):
-    NODE_RADIUS = 20
-    EDGE_DIST = 26
-    EDGE_HEAD_LEN = 32
 
     def __init__(self):
         super().__init__()
@@ -111,6 +104,65 @@ class SignalWidget(QWidget):
             self.vboxdata.addWidget(elwidget)
         self.vboxdata.addStretch()
 
+class SignalTable(QTableWidget):
+    """Widget for displaying contents of edges and firing of nodes."""
+    def __init__(self):
+        super().__init__()
+
+        self.setRowCount(3)
+        self.setColumnCount(1)
+        self.setVerticalHeaderLabels(['a', 'b', 'c'])
+        self.setGridStyle(Qt.NoPen)
+        self.setHorizontalScrollMode(QAbstractItemView.ScrollPerPixel)
+        self.setSortingEnabled(True)
+
+        hheader = self.horizontalHeader()
+        hheader.setVisible(False)
+        hheader.setSectionResizeMode(QHeaderView.ResizeToContents)
+
+        vheader = self.verticalHeader()
+        vheader.setSectionResizeMode(QHeaderView.ResizeToContents)
+
+        vheader.setSectionsMovable(True)
+        # vheader.setDragEnabled(True)
+        # vheader.setDragDropMode(QAbstractItemView.InternalMove)
+
+        self.pbButton1 = QPushButton('set width to 100')
+        self.pbButton1.setMinimumWidth(80)
+        self.pbButton1.setFixedHeight(24)
+        self.pbButton1.setStyleSheet('background-color: red;')
+        self.pbButton1.clicked.connect(self.btnClicked)
+        self.pbButton2 = QPushButton('set width to 200')
[…]

### 2016-09-15 mainwindow.py
Placing new table based signalwidget in mainwindow.

@@ -16,7 +16,7 @@ from PyQt5.QtGui import QIcon
 from csdfgraph import CSDFGraph, G0
 from runwindow import RunWindow
 from logwidget import LogWidget
-from signalwindow import SignalWidget
+from signalwindow import SignalWidget, SignalTable
 from graphicsview import GraphWidget
 
 from codegen.clashcodegen import ClashCodeGen
@@ -102,7 +102,7 @@ class MainWindow(QMainWindow):
         self.addDockWidget(Qt.LeftDockWidgetArea, self.dwRunWindow)
 
         self.dwSignalWindow = QDockWidget('Edge signals', self)
-        self.signalWindow = SignalWidget()
+        self.signalWindow = SignalTable()
         self.signalWindow.setMinimumHeight(250)
         self._updateSignalWindow()
         self.dwSignalWindow.setAllowedAreas(Qt.BottomDockWidgetArea)

### 2016-09-15 signalwindow.py

@@ -10,7 +10,7 @@ author: Rinse Wester
 
 from PyQt5.QtWidgets import QApplication, QWidget, QLayout, QVBoxLayout, QHBoxLayout, QLabel, QScrollArea, QTableWidget, QAbstractItemView, QHeaderView, QPushButton
 from PyQt5.QtCore import Qt, QRect, QPoint
-from PyQt5.QtGui import QPainter, QFont, QPen, QBrush, QPolygon
+from PyQt5.QtGui import QPainter, QFont, QPen, QBrush, QPolygon, QColor
 import sys
 
 
@@ -83,7 +83,7 @@ class SignalWidget(QWidget):
         # Create the edge labels and put in layout
         for lbl in lbls:
             lblwidget = QLabel(lbl)
-            lblwidget.setMinimumHeight(24)
+            lblwidget.setMinimumHeight(20)
             self.vboxlabels.addWidget(lblwidget)
         self.vboxlabels.addStretch()
 
@@ -100,7 +100,7 @@ class SignalWidget(QWidget):
         for edata in data:
             elwidget = EdgeLogWidget()
             elwidget.setTokenData(edata)
-            elwidget.setMinimumHeight(24)
+            elwidget.setMinimumHeight(20)
             self.vboxdata.addWidget(elwidget)
         self.vboxdata.addStretch()
 
@@ -109,9 +109,7 @@ class SignalTable(QTableWidget):
     def __init__(self):
         super().__init__()
 
-        self.setRowCount(3)
         self.setColumnCount(1)
-        self.setVerticalHeaderLabels(['a', 'b', 'c'])
         self.setGridStyle(Qt.NoPen)
         self.setHorizontalScrollMode(QAbstractItemView.ScrollPerPixel)
         self.setSortingEnabled(True)
@@ -122,30 +120,51 @@ class SignalTable(QTableWidget):
 
         vheader = self.verticalHeader()
         vheader.setSectionResizeMode(QHeaderView.ResizeToContents)
-
         vheader.setSectionsMovable(True)
-        # vheader.setDragEnabled(True)
-        # vheader.setDragDropMode(QAbstractItemView.InternalMove)
 
-        self.pbButton1 = QPushButton('set width to 100')
-        self.pbButton1.setMinimumWidth(80)
-        self.pbButton1.setFixedHeight(24)
[…]

### 2016-09-16 mainwindow.py
The signal log is now completely replaced by the new QtableWdidget-based viewer.

@@ -16,7 +16,7 @@ from PyQt5.QtGui import QIcon
 from csdfgraph import CSDFGraph, G0
 from runwindow import RunWindow
 from logwidget import LogWidget
-from signalwindow import SignalWidget, SignalTable
+from signalwindow import SignalTable
 from graphicsview import GraphWidget
 
 from codegen.clashcodegen import ClashCodeGen
@@ -103,7 +103,6 @@ class MainWindow(QMainWindow):
 
         self.dwSignalWindow = QDockWidget('Edge signals', self)
         self.signalWindow = SignalTable()
-        self.signalWindow.setMinimumHeight(250)
         self._updateSignalWindow()
         self.dwSignalWindow.setAllowedAreas(Qt.BottomDockWidgetArea)
         self.dwSignalWindow.setWidget(self.signalWindow)
@@ -127,14 +126,11 @@ class MainWindow(QMainWindow):
 
     def _updateSignalWindow(self):
 
-        edgeNames = []
-        edgeData = []
         if self.graph is not None:
-            for (src, dst), edata in self.graph.edgestates.items():
-                edgeNames.append(src + ' → ' + dst)
-                edgeData.append(edata)
-        self.signalWindow.setEdgeLabels(edgeNames)
-        self.signalWindow.setEdgeData(edgeData)
+            self.signalWindow.clearSignals()    
+            for (src, dst), signaldata in self.graph.edgestates.items():
+                signalname =  src + ' → ' + dst
+                self.signalWindow.addSignal(signalname, signaldata)
 
     def openActionTriggered(self):
 

### 2016-09-16 runwindow.py

@@ -91,7 +91,6 @@ class RunWindow(QWidget):
             self.graph.back()
         elif self.sender() == self.btnNext:
             self.graph.step()           
-
         else:
             # btnRunUntill button clicked
             src, dst = self.cmbEdges.currentText().split(' → ')
@@ -103,17 +102,17 @@ class RunWindow(QWidget):
             if n == MAX_ITERATIONS:
                 Log.addLogMessage(Log.WARNING, 'Stop condition never met')
 
-
         self.lblStateNr.setText('State: ' + str(self.graph.stateCount() - 1))
         self.btnBack.setEnabled(self.graph.stateCount() > 1)
         self.btnReset.setEnabled(self.graph.stateCount() > 1)
 
         # Display the new state of the graph in the GraphWidget
-        #self.gwid.update()
         self.graphWidget.updateTokensGraph()
 
-        # update the log window such that all tokens of all states are shown
-        self.swid.setEdgeData(list(self.graph.edgestates.values()))
+        # update the signal window such that all tokens of all states are shown
+        for (src, dst), signaldata in self.graph.edgestates.items():
+                signalname =  src + ' → ' + dst
+                self.swid.updateSignal(signalname, signaldata)
 
     def setGraphWidget(self, gwid):
 

### 2016-09-16 signalwindow.py

@@ -8,101 +8,11 @@ author: Rinse Wester
 
 """
 
-from PyQt5.QtWidgets import QApplication, QWidget, QLayout, QVBoxLayout, QHBoxLayout, QLabel, QScrollArea, QTableWidget, QAbstractItemView, QHeaderView, QPushButton
+from PyQt5.QtWidgets import QApplication, QWidget, QLabel, QScrollArea, QTableWidget, QAbstractItemView, QHeaderView, QPushButton
 from PyQt5.QtCore import Qt, QRect, QPoint
 from PyQt5.QtGui import QPainter, QFont, QPen, QBrush, QPolygon, QColor
 import sys
-
-
-class SignalWidget(QWidget):
-
-    def __init__(self):
-        super().__init__()
-
-        self.lblEdgesHeader = QLabel('<b>Edge</b>', self)
-        self.lblEdgesHeader.setMinimumWidth(80)
-        self.lblEdgesHeader.setMaximumWidth(80)
-
-        self.lblDataHeader = QLabel('<b>Data</b>', self)
-
-        self.hboxHeader = QHBoxLayout()
-        self.hboxHeader.addWidget(self.lblEdgesHeader)
-        self.hboxHeader.addWidget(self.lblDataHeader)
-
-        # create an empty vbox layout to hold the edge labels
-        self.vboxlabels = QVBoxLayout()
-        self.vboxlabels.setContentsMargins(0, 0, 0, 0)
-        self.vboxlabels.setSizeConstraint(QLayout.SetMinAndMaxSize)
-
-        self.lblswidget = QWidget(self)
-        self.lblswidget.setMinimumWidth(80)
-        self.lblswidget.setMaximumWidth(80)
-        self.lblswidget.setLayout(self.vboxlabels)
-
-        # create an empty vbox
-        self.vboxdata = QVBoxLayout()
-        self.vboxdata.setContentsMargins(0, 0, 0, 0)
-        self.vboxdata.setSizeConstraint(QLayout.SetMinAndMaxSize)
-
-        self.datascrollwidget = QScrollArea()
-        self.datascrollwidget.setAutoFillBackground(True)
-        p = self.datascrollwidget.palette()
-        p.setColor(self.datascrollwidget.backgroundRole(), Qt.white)
-        self.datascrollwidget.setPalette(p)
-        self.datawidget = QWidget()
-        self.datawidget.setLayout(self.vboxdata)
[…]

### 2016-09-16 runwindow.py
Added autoscrolling such that the lastest data is always shown.

@@ -10,6 +10,7 @@ author: Rinse Wester
 
 import sys
 from PyQt5.QtWidgets import QWidget, QApplication, QVBoxLayout, QHBoxLayout, QPushButton, QLabel, QComboBox, QLineEdit
+from PyQt5.QtCore import QTimer
 from log import Log
 
 class RunWindow(QWidget):
@@ -113,6 +114,11 @@ class RunWindow(QWidget):
         for (src, dst), signaldata in self.graph.edgestates.items():
                 signalname =  src + ' → ' + dst
                 self.swid.updateSignal(signalname, signaldata)
+        
+        # Nasty way to make sure the widget scrolls to the end
+        # required because the max value of the scrollbar is not enought due
+        # to delayed resizing of the tableWidget...
+        QTimer.singleShot(1, self.swid.scrollToEnd)
 
     def setGraphWidget(self, gwid):
 

### 2016-09-16 signalwindow.py

@@ -12,6 +12,7 @@ from PyQt5.QtWidgets import QApplication, QWidget, QLabel, QScrollArea, QTableWi
 from PyQt5.QtCore import Qt, QRect, QPoint
 from PyQt5.QtGui import QPainter, QFont, QPen, QBrush, QPolygon, QColor
 import sys
+import random as rdm
 from collections import OrderedDict
 
 class SignalTable(QTableWidget):
@@ -34,15 +35,6 @@ class SignalTable(QTableWidget):
 
         # ordered dictionay to keeps refs to data and signal widget
         self.refDict = OrderedDict({})
-
-        self.addSignal('Alpha', [[1], [1,2], [], [3]])
-        self.addSignal('Beta', [[1,2], [1,2], [1], []])
-        self.clearSignals()
-        self.addSignal('Een', [[1,2,3], [], [], []])
-        self.addSignal('Twee', [[1,2,3], [4,5,6], [], []])
-        self.addSignal('Drie', [[1,2,3], [4,5,6], [7,8,9], []])
-        self.removeSignal('Twee')
-        self.updateSignal('Drie', [[1],[1,2],[1,2,3],[1,2,3,4],[1,2,3,4,5]])
 
     def _signalIndex(self, signalname):
         return list(self.refDict.keys()).index(signalname)
@@ -82,7 +74,11 @@ class SignalTable(QTableWidget):
         self.resizeColumnsToContents()
         self.resizeRowsToContents()
 
-            
+    def scrollToEnd(self):
+        hScrollBar = self.horizontalScrollBar()
+        maxval = hScrollBar.maximum()
+        hScrollBar.setValue(maxval)
+
 class SignalLogWidget(QWidget):
 
     STATE_WIDTH = 100
@@ -267,8 +263,18 @@ class SignalLogWidget(QWidget):
 if __name__ == '__main__':
 
     app = QApplication(sys.argv)
-    ex = SignalTable()
-    ex.show()
+    sw = SignalTable()
+    sw.show()
+
+    for i in range(100):
+        signalname = 'Signal-' + str(i)
+        signaldata = []
+        for i in range(100):
+            tokens = [1,2,3,4]
+            rdm.shuffle(tokens)
+            signaldata.append(tokens)
+        sw.addSignal(signalname, signaldata)
+
     app.exec_()
     app.deleteLater()
     sys.exit()

### 2016-09-17 signalwindow.py
Working on highlighting of cycles in the signalwwidget. For the data it works but for the transition it still has to be implemented.

@@ -13,6 +13,7 @@ from PyQt5.QtCore import Qt, QRect, QPoint
 from PyQt5.QtGui import QPainter, QFont, QPen, QBrush, QPolygon, QColor
 import sys
 import random as rdm
+from math import floor
 from collections import OrderedDict
 
 class SignalTable(QTableWidget):
@@ -88,7 +89,6 @@ class SignalLogWidget(QWidget):
     SIGNAL_COLOR_HOVER = QColor(74, 73, 80)
     TEXT_COLOR = QColor(194, 194, 195)
 
-
     def __init__(self):
 
         super().__init__()
@@ -97,14 +97,12 @@ class SignalLogWidget(QWidget):
         p = self.palette()
         p.setColor(self.backgroundRole(), Qt.white)
         self.setPalette(p)
-
         self.setMouseTracking(True)
-
         self.setMinimumHeight(20)
 
         self.tokenData = [[1, 2, 3], [1, 2]]
-
         self.zoomFactor = 1.0
+        self.hoveringCycle = None
 
     def _updateSize(self):
 
@@ -127,8 +125,16 @@ class SignalLogWidget(QWidget):
         self.update()
 
     def mouseMoveEvent(self, event):
-        # TODO: put highlighting code here....
-        pass
+        
+        xpos = event.pos().x()
+        self.hoveringCycle = floor((xpos + self.TRANSITION_WIDTH / 2) / (self.STATE_WIDTH * self.zoomFactor + self.TRANSITION_WIDTH))
+        self.update()
+
+    def leaveEvent(self, event):
+
+        self.hoveringCycle = None
+        self.update()
+        super().leaveEvent(event)
 
     def paintEvent(self, e):
 
@@ -145,7 +151,7 @@ class SignalLogWidget(QWidget):
 
             beginCoor = i * (curStatewidth + self.TRANSITION_WIDTH)
 
-            self._drawState(qp, beginCoor, curStatewidth, tokenData)
+            self._drawState(qp, beginCoor, curStatewidth, tokenData, i == self.hoveringCycle)
 
             if tokenData == self.tokenData[i + 1]:
                 if tokenData == []:
@@ -230,12 +236,17 @@ class SignalLogWidget(QWidget):
             qp.setPen(pen)
             qp.drawLine(xpos, h / 2, xpos + width, h / 2)
 
-    def _drawState(self, qp, xpos, width, data):
+    def _drawState(self, qp, xpos, width, data, hovering=False):
 
[…]
